\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-16 related.tex
update in related work

A significant amount of research has been conducted on how to analyze and test distributed systems~\cite{lamport1994temporal, schuppan2004efficient, killian2007life, gupta2008diecast, yang2009modist}, but a lot of these techniques either have significant limitations, or cannot be easily applied in a production environment, due to many complexities that are outside the scope of a research project.

@@

In Verdi~\cite{wilcox2015verdi}, a distributed system is written and verified in Coq, and then OCaml code is produced for execution. Verdi cannot find liveness bugs. \psharp is also more production-friendly (works on a mainstream language). \PDComment{say few more stuff}

D3S~\cite{liu2008d3s} \PDComment{should read the paper, they say they are debugging running systems}

>>>>

\psharp is most closely related to \textsc{MoDist}~\cite{yang2009modist}, a model checker that can be applied on unmodified distributed systems. To achieve this, the tool uses binary instrumentation (reuses the instrumentation engine of the D$^3$S testing tool) to expose all actions of the system under test, and then uses a model checking engine to systematically explore these actions. \textsc{MoDist} also provides a virtual clock manager that can simulate timeouts and accelerate the passage of time. A major limitation of \textsc{MoDist} is that it must be applied on a whole system, which does not scale for production systems. In contrast, \psharp has built-in support for modeling the environment of individual components of a system, which allows the tool to achieve scalability. Further, \psharp is an extension of the \csharp language and has built-in systematic testing support; it does not need to perform binary instrumentation which can be computationally expensive.

\textsc{MaceMc}~\cite{killian2007life} is a model checker for distributed systems implemented in the \textsc{Mace} language. The focus of \textsc{MaceMc} is to find liveness property violations using an algorithm based on bounded random walk and the use of heuristics. \psharp differs from \textsc{MaceMc} in that it can be applied on legacy code written in a mainstream language, whereas a system to be tested with \textsc{MaceMc} has to be written in \textsc{Mace}, which makes \textsc{MaceMc} harder to be applied in an industrial setting. Further, \psharp uses a simpler, but effective, algorithm for detecting liveness bugs.

\textsc{Fate} and \textsc{Destini} is a framework for systematically injecting (combination of) failures in distributed systems~\cite{gunawi2011fate}.

DieCast~\cite{gupta2008diecast}

@@

Another approach is Verdi~\cite{wilcox2015verdi}, where a distributed system is written and verified in Coq, and then OCaml code is produced for execution. Verdi cannot find liveness bugs. \psharp is also more production-friendly: it works on \csharp, which is a mainstream language.
